%This is a comment.  It will not appear in the compiled file.

\documentclass[10pt]{article}

\usepackage[normalem]{ulem}

\title{Use Cases}
\author{The Four Boss}



\date{ 11 July 2019}

\begin{document}
\maketitle
\tableofcontents
\section*{Use case 1:Budget management}
\subsection{Goal}
To enable The Project Manager to study the Budget and split the Budget within all tasks assigned
\subsection{Actors}
The Project Manager and the Database and The User 
\subsection{Scenario}
\begin{enumerate}
\item Step1. The user/PM logs onto the Web Application via the URL.
\item Step2. Protected Authetication
\item Step3.Asking the user to split how much quantity for a Particular task.
\item Step4.To give Alerts when the user reaches OVER BUDGET.
\end{enumerate}


\section*{Use case 2: Track Resources Management}
\subsection{Goal}
To enable The Project Manager to study the Budget and utilize it EFFICIENTLY
\subsection{Actors}
The Project Manager and the Database and The User 
\subsection{Scenario}
\begin{enumerate}
\item Step1. The user/PM logs onto the Web Application via the URL.
\item Step2. Protected Authetication
\item Step3.To create the Resources Backlog
\item Step4.To create the database of all resources 
\end{enumerate}


\section*{Use Case 1: Database Tool must assists Project Manager }
\subsection{GOAL}
To analysing, specifying, or even modifying database system which can help Project Manager manages the database more effectively.
\subsection{Actors}
1. Project Management \\
2. Project Manager \\
3. Management Database Tool. 
\subsection{Scenerio}
\begin{enumerate}
\item Step1. PM might facilitate faster data retrieval 
\item Step2. More Quick Tips for PM to boost the adequate 
\item Step3. PM can add , delete or adjusting database by using THIS Database Tool
\end{enumerate}

\section * {Use Case :Analyizing Data}
\subsection * {Goal}
The Project Management database must Compare the latest data with previoulsy stored data to track progress
\subsection * {Actors}
1.The Project Management Tool\\
2.The Database\\
3.The Project Manager

\subsection * {Scenario}
\begin{enumerate}
\item Step1.All the filles must be encrypted.
\item Step2.If User closes the Program then the program must autosave all files.
\item Step3.A percentage bar must be shown indicating the progress of the project
\end{enumerate}


\end{document}
